Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-02 manuscript.Rmd
Call joined CRPs

```{r plot-rp-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of all events from target filtered data.'}

# call image
knitr::include_graphics("./results/primary/crqa/target-rp-all_events.png")

```{r plot-rp-targ-pos, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of positive events from target filtered data.'}

# call image
knitr::include_graphics("./results/primary/crqa/target-rp-pos_events.png")

```{r plot-rp-targ-neg, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of negative events from target filtered data.'}

# call image
knitr::include_graphics("./results/primary/crqa/target-rp-neg_events.png")

@@

```{r plot-rp-source-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of all events from source and target filtered data.'}

# call image
knitr::include_graphics("./results/primary/crqa/source_target-rp-all_events.png")

```{r plot-rp-source-targ-pos, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of positive events from source and target filtered data.'}

# call image
knitr::include_graphics("./results/primary/crqa/source_target-rp-pos_events.png")

```{r plot-rp-source-targ-neg, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of negative events from source and target filtered data.'}

# call image
knitr::include_graphics("./results/primary/crqa/source_target-rp-neg_events.png")

>>>>

```{r plot-rp-targ, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of all events from target filtered data.'}

# call image
knitr::include_graphics("./results/primary/crqa/target-rp-joined.png")

@@

```{r plot-rp-source-targ, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of all events from source and target filtered data.'}

# call image
knitr::include_graphics("./results/primary/crqa/source_target-rp-joined.png")
